Paper Figs

### 2023-06-01 graphs_newt_snakes/Paper_figs.Rmd
I have updated some figures

file$exp = factor(file$exp, levels=c("Flat Map", "Cost Gradent Map", "Interaction Gradent Map"))

@@

@@

plot1 <-   ggplot(file) +
  labs(subtitle = "Snake")+
  geom_boxplot(aes(x=factor(snake_GA), y=snake_pheno_change, fill=newt_GA))+
  ylab(y_label) + 
  xlab("Snake GA")+
  ylim(0,6)+
 scale_x_discrete(labels=c("1e-08_0.005" = "GA 1", "1e-09_0.05" = "GA 2", "1e-10_0.5" = "GA 3",
                             "1e-11_5" = "GA 4"))+
     theme(plot.title = element_text(size=5)) +
  #scale_fill_discrete(fornewt, labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
  scale_fill_manual(values = rev(fornewt), labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
   #scale_fill_brewer(fornewt , labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
  #scale_alpha(guide = 'none')+
    #labs(fill = " ")+
  guides(fill=guide_legend(title="Newt GA"))+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18), 
                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))

plot2 <-   ggplot(file) +
 labs(subtitle = "Newt")+
  geom_boxplot(aes(x=factor(newt_GA), y=newt_pheno_change, fill=snake_GA))+
  ylab(" ")+ 
  xlab("Newt GA")+
  ylim(0,6)+
 scale_x_discrete(labels=c("1e-08_0.005" = "GA 1", "1e-09_0.05" = "GA 2", "1e-10_0.5" = "GA 3",
                             "1e-11_5" = "GA 4"))+
     theme(plot.title = element_text(size=5)) +
  #scale_fill_discrete(labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
  #scale_fill_brewer(forsnake)+
  scale_fill_manual(values = forsnake, labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
  #scale_alpha(guide = 'none')+
    #labs(fill = " ")+
  guides(fill=guide_legend(title="Snake GA"))+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18), 
                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))

@@

file$coevo_speed[file$sim %in% choices[1]] = "Fast Coevolution"
file$coevo_speed[file$sim %in% choices[2]] = "Slow Coevolution"
file$coevo_speed[file$sim %in% choices[3]] = "No Coevolution"
file$coevo_speed = factor(file$coevo_speed, levels=c("Fast Coevolution", "Slow Coevolution", "No Coevolution"))
plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==0),]) +
    facet_wrap(~coevo_speed, ncol=1)+
    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
    geom_line(aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno"),)+#group=rep
    geom_line(aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno"))+#group=rep
    #ylim(-1.,2.5)+
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Species",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18),
                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
  return(plot)

@@

>>>>

#smallset = file[which(file$gen>=40000 & file$gen<=50000 & file$exp=="Cost Gradent Map" & file$cor_score=="True"),]
file$exp = factor(file$exp, levels=c("Flat Map", "Cost Gradent Map", "Interaction Gradent Map"))

@@

point_coevo_start_stop_flat_map <- function(file, title, subt, x_label, y_label){

plot1 <-   ggplot(file) +
  labs(subtitle = "Start")+
  xlab(x_label) + ylab(y_label)+
  ylim(0,10)+
  geom_point(aes(x=factor(sim, level=c("A", "B", "E", "C", "I", "D", "M", "F", "G", "J", "H", "N", "K", "L", "O", "P")), y=as.numeric(N_pheno_start)), color="darkred")+

    geom_point(aes(x=factor(sim, level=c("A", "B", "E", "C", "I", "D", "M", "F", "G", "J", "H", "N", "K", "L", "O", "P")), y=as.numeric(S_pheno_start)), color="steelblue")+

     theme(plot.title = element_text(size=5)) +
    labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18), 
                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))

plot2 <-   ggplot(file) +
  labs(subtitle = "End")+
  xlab(x_label) + ylab(y_label)+
  ylim(0,10)+
  geom_point(aes(x=factor(sim, level=c("A", "B", "E", "C", "I", "D", "M", "F", "G", "J", "H", "N", "K", "L", "O", "P")), y=as.numeric(N_pheno_end)), color="darkred")+

  geom_point(aes(x=factor(sim, level=c("A", "B", "E", "C", "I", "D", "M", "F", "G", "J", "H", "N", "K", "L", "O", "P")), y=as.numeric(S_pheno_end)), color="steelblue")+

     theme(plot.title = element_text(size=5)) +
    labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18), 
                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))

myplot = ggarrange(plot1, plot2, ncol = 2) + plot_annotation(title = title) & theme(title = element_text( size=18,face = 'bold')) #top=grid::textGrob("title"))

@@

plot1 <-   ggplot(file) +
  labs(subtitle = "Snake Phenotype Change")+
  geom_boxplot(aes(x=factor(snake_GA), y=snake_pheno_change, fill=newt_GA))+
  ylab(y_label) + 
  xlab("Snake GA")+
  ylim(0,6)+
 scale_x_discrete(labels=c("1e-08_0.005" = "1", "1e-09_0.05" = "2", "1e-10_0.5" = "3",
                             "1e-11_5" = "4"))+
     theme(plot.title = element_text(size=5)) +
  #scale_fill_discrete(fornewt, labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
  scale_fill_manual(values = rev(fornewt), labels=c('1', '2', '3', '4'))+
   #scale_fill_brewer(fornewt , labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
  #scale_alpha(guide = 'none')+
    #labs(fill = " ")+
  guides(fill=guide_legend(title="Newt GA"))+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 14), 
                      title =element_text(size=14, face='bold'), legend.text=element_text(size=12), strip.text.x = element_text(size = 16))

plot2 <-   ggplot(file) +
 labs(subtitle = "Newt Phenotype Change")+
  geom_boxplot(aes(x=factor(newt_GA), y=newt_pheno_change, fill=snake_GA))+
  ylab(" ")+ 
  xlab("Newt GA")+
  ylim(0,6)+
 scale_x_discrete(labels=c("1e-08_0.005" = "1", "1e-09_0.05" = "2", "1e-10_0.5" = "3",
                             "1e-11_5" = "4"))+
     theme(plot.title = element_text(size=5)) +
  #scale_fill_discrete(labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
  #scale_fill_brewer(forsnake)+
  scale_fill_manual(values = forsnake, labels=c('1', '2', '3', '4'))+
  #scale_alpha(guide = 'none')+
    #labs(fill = " ")+
  guides(fill=guide_legend(title="Snake GA"))+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 14), 
                      title =element_text(size=14, face='bold'), legend.text=element_text(size=12), strip.text.x = element_text(size = 16))

@@

file$coevo_speed[file$sim %in% choices[1]] = "Fast Evolution"
file$coevo_speed[file$sim %in% choices[2]] = "Slow Evolution"
file$coevo_speed[file$sim %in% choices[3]] = "No Evolution"
file$coevo_speed = factor(file$coevo_speed, levels=c("Fast Evolution", "Slow Evolution", "No Evolution"))
plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==0),]) +
    facet_wrap(~coevo_speed, ncol=1)+
    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
    geom_line(aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno"),)+#group=rep
    geom_line(aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno"))+#group=rep
    #ylim(-1.,2.5)+
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Species",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18),
                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
  return(plot)

@@

title = "Phenotype Start and Stop Coevolution FLat Map"
point_coevo_start_stop_flat_map(file3, title, subt, x_label, y_label)
